\vspace{-15mm}\fontsize{16pt}{10pt}\selectfont\textbf{Facial Expression Recognition with\\ Convolutional Neural Networks}

### 2018-04-17 doc/paper.tex
remove vgg reference

In simple CNNs, it is common to combine convolutional and pooling layers to compute feature activations while reducing dimensionality. During the designing process, it turned out that stacking multiple convolutional layers in a VGG-Fashion \cite{simonyan14} improved the model accuracy on the test set by about 20 percent compared to alternating pooling and convolutional layers.

@@

\section{Discussion and Conclusion}

>>>>

In simple CNNs, it is common to combine convolutional and pooling layers to compute feature activations while reducing dimensionality. During the designing process, it turned out that stacking multiple convolutional layers improved the model accuracy on the test set by about 20 percent compared to alternating pooling and convolutional layers.

@@

\section{Conclusion and Discussion}
